---
title: "Week 8 Lab Questions"
output:
  pdf_document: default
  html_document: default
---


## Generate a linearly separable dataset.

```{r}

set.seed(300)
x.pos <- matrix(rnorm(100*2,mean=0), nrow = 100, ncol = 2)
set.seed(300)
x.neg <- matrix(rnorm(100*2,mean=3), nrow = 100, ncol = 2)
y <- c(rep(1,100),rep(-1,100))
x <- rbind(x.pos,x.neg)
dat <- data.frame(x = x, y = as.factor(y))

plot(x, col = ifelse(y>0,1,2))
legend("topleft",c("Positive","Negative"),col=seq(2),pch=1,text.col=seq(2))

#####Produce training and testing datasets#####
set.seed(300) 
train <-  sample(200, 200*0.7)
dat.train <-  dat[train,]
x.test <- x[-train,]
y.test <- y[-train]

```

#### 1)	Install and load the library `e1071`.
```{r}

```

#### 2)	Build a linear SVM model with `cost = 1`.
```{r}

```

#### 3)	Report how many support vectors are from each class respectively.
```{r}

```

#### 4)	Plot the svm model and check how many support vectors are on the wrong side of the boundary and how many data points are very close to the margin.
```{r}

```

#### 5)	Predict the class label of `y` on the testing dataset and estimate the testing error rate.
```{r}

```

#### 6)	Now try a smaller `cost = 0.01` and a larger `cost = 1e5` and repeat step 2)-5). 
```{r}

```

#### 7)	Use `tune()` function to select the best model (tune the parameter `C` or `cost`). Set seed to be 1.
```{r}

```


## Generate a linearly inseparable dataset.
```{r}

set.seed(300)
x.pos1 <- matrix(rnorm(30*2,mean=0), nrow=30, ncol=2)
x.pos2 <- matrix(rnorm(30*2,mean=3), nrow=30, ncol=2)
set.seed(300)
x.neg1 <- matrix(c(rnorm(30,mean=0)+3,rnorm(30,mean=0)),nrow=30,ncol=2)
x.neg2<- matrix(c(rnorm(30,mean=3)-3,rnorm(30,mean=3)),nrow=30,ncol=2)
y <- c(rep(1,60),rep(-1,60))
x <- rbind(x.pos1, x.pos2, x.neg1, x.neg2)
dat2 <- data.frame(x = x, y = as.factor(y))


plot(x, 
     col = ifelse(y > 0, 1, 2), 
     pch = ifelse(y > 0, 1, 2))
legend("topleft", 
       c("Positive","Negative"), 
       col = seq(2), 
       pch = 1:2, 
       text.col = seq(2))

#####Produce training and testing datasets#####
set.seed(300)
train <- sample(120, 120*0.7)  
dat2.train <- dat2[train,]
x.test <- x[-train,]
y.test <- y[-train]
```

#### 8)	Build an SVM model with a radial kernel, `gamma = 1` and `cost = 1`. In this model, a) see the summary; b) plot the svm and c) estimate the testing error rate.

```{r}

```

#### 9)	Build an SVM model with a radial kernel, `gamma = 1` and `cost = 1e5`. In this model, a) see the summary; b) plot the svm and c) estimate the testing error rate.
```{r}

```

#### 10)	Choose the best choice of `gamma` and `cost` for an SVM with a radial kernel. 
```{r}

```

#### 11)	Use the best model to estimate the testing error rate.
```{r}

```

