---
title: "Week 4 Lab Questions"
output:
  pdf_document: default
---

## Problem Statement
A researcher is interested in how variables, such as GRE (Graduate Record Exam scores), GPA (grade point
average) and rank (prestige of the undergraduate institution), affect admission into graduate school. The
response variable, admit/do not admit, is a binary variable.

## Dataset
The dataset is included in the package aod. Install the package using the command install.packages("aod"), and include package using the command library(aod).
Using the following command to load the dataset
```{r}
mydata <- read.csv("https://stats.idre.ucla.edu/stat/data/binary.csv")
## view the first few rows of the data
head(mydata)
```

[More on reading and writing CSV files, see here: https://swcarpentry.github.io/r-novice-inflammation/
11-supp-read-write-csv/index.html]
This dataset has a binary response (outcome, dependent) variable called admit. There are three predictor
variables: gre, gpa and rank. We will treat the variables gre and gpa as continuous. The variable rank
takes on the values 1 through 4. Institutions with a rank of 1 have the highest prestige, while those with a
rank of 4 have the lowest.

## Questions

#### 1)	Get basic descriptives for the entire data set using `summary()`. View the dataset using `View()`. Get the binary values of class label admit using 'mydata$admit'.
```{r}

```

#### 2)	How many observations are there in this dataset? 
```{r}

```

#### 3)	Get the standard deviations. Hint: use sapply to apply the sd function to each variable in the dataset: `sapply(mydata, sd)`. Now get the mean for the first three variables (i.e., `admit`, `gre` and `gpa`) in a similar way.
```{r}

```

#### 4)	Convert `rank` to a factor to indicate that rank should be treated as a categorical variable. 
```{r}

```

#### 5)	Estimate a logistic regression model using the `glm` function, and get the results using the `summary` command. 

```{r}

```

#### 6)	Do you notice variable `rank` is replaced with categorical variables `rank2`, `rank3`, and `rank4` that can only take values of 0 or 1? Recall that the original variable `rank` can take values of 1, 2, 3, or 4. Why isn't a variable `rank1` needed? If rank is 1, what are the values of `rank2`, `rank3` and `rank4`?


#### 7)	From the z-statistics and p-values of the variables, report which variables are statistically significant. 


#### 8)	Use the model to predict the training dataset and store the results to a vector of probabilities `admit.prob`.
```{r}

```

#### 9)	Create another vector `admit.pred` to show 0 or 1 for `admit.prob`. Let's set the value to be 0 if the probability is less than 0.5, and 1 if the probability is no less than 0.5.
```{r}

```

#### 10)	Using `table()` function to create a confusion matrix to determine how many observations were correctly or incorrectly classified. Calculate the percentage that the observations were correctly classified.
```{r}

```

#### 11)	Use the model to predict the average cases in each rank, that is, four new data with (mean gre), (mean gpa) and (rank from 1 to 4). 
```{r}

```



For more exercises and more detailed explanations, please refer to https://stats.idre.ucla.edu/r/dae/logit-regression/.



