---
title: "Week 4 Lab Solutions"
output:
  pdf_document: default
---
To load the data:
```{r}
#install.packages("aod")
library(aod)
mydata <- read.csv("https://stats.idre.ucla.edu/stat/data/binary.csv")
#mydata <- read.csv("D:/binary.csv")
head(mydata)
```

#### 1)	Get basic descriptives for the entire data set using `summary()`. View the dataset using `View()`. Get the binary values of class label admit using 'mydata$admit'.
```{r}
summary(mydata)
View(mydata)
mydata$admit
```

#### 2)	How many observations are there in this dataset? 
```{r}
nrow(mydata)
```

#### 3)	Get the standard deviations. Hint: use sapply to apply the sd function to each variable in the dataset: `sapply(mydata, sd)`. Now get the mean for the first three variables (i.e., `admit`, `gre` and `gpa`) in a similar way.
```{r}
sapply(mydata, sd)
sapply(mydata[,-4], mean)
```
`mydata[,-4]` indicates all the rows and all the columns except for the 4th column (the `rank`). We exclude rank as it is a categorical variable and calculating its mean is not appropriate.  

#### 4)	Convert `rank` to a factor to indicate that rank should be treated as a categorical variable. 
```{r}
mydata$rank <- factor(mydata$rank)
mydata$rank
```

#### 5)	Estimate a logistic regression model using the `glm` function, and get the results using the `summary` command. 
```{r}
glm.admit.fit <- glm(admit ~ gre + gpa + rank, 
                     data = mydata, 
                     family = "binomial"
                     )
summary(glm.admit.fit)
```

#### 6)	Do you notice variable `rank` is replaced with categorical variables `rank2`, `rank3`, and `rank4` that can only take values of 0 or 1? Recall that the original variable `rank` can take values of 1, 2, 3, or 4. Why isn't a variable `rank1` needed? If rank is 1, what are the values of `rank2`, `rank3` and `rank4`?

If `rank` is 1, then `rank2` is 0, `rank3` is 0 and `rank4` is 0.

If `rank` is 2, then `rank2` is 1, `rank3` and `rank4` are 0.

If `rank` is 3, then `rank2` is 0, `rank3` is 1 and `rank4` is 0.

If `rank` is 4, then `rank2` and `rank3` are 0 and `rank4` is 1.


#### 7)	From the z-statistics and p-values of the variables, report which variables are statistically significant. 

The z-statistics of all the variables are large and the p-values of all the variables are small (<0.05). All the variables are statistically significant.


#### 8)	Use the model to predict the training dataset and store the results to a vector of probabilities `admit.prob`.
```{r}
admit.prob <- predict(glm.admit.fit, type = "response")
head(admit.prob)
```
Note that this is a vector of probabilities. `admit` in the original dataset has values 0 or 1 (0 for reject and 1 for admitted).

#### 9)	Create another vector `admit.pred` to show 0 or 1 for `admit.prob`. Let's set the value to be 0 if the probability is less than 0.5, and 1 if the probability is no less than 0.5.
```{r}
admit.pred <- rep(1,400)
admit.pred[admit.prob<0.5] <- 0
head(admit.pred)
```

#### 10)	Using `table()` function to create a confusion matrix to determine how many observations were correctly or incorrectly classified. Calculate the percentage that the observations were correctly classified.
```{r}
table(admit.pred, mydata$admit)
mean(admit.pred == mydata$admit)
```

#### 11)	Use the model to predict the average cases in each rank, that is, four new data with (mean gre), (mean gpa) and (rank from 1 to 4). 
```{r}
newdata1 <- with(mydata, 
                 data.frame(gre = mean(gre), 
                            gpa = mean(gpa), 
                            rank = factor(1:4)
                            )
                 )
newdata1
newdata1$admit1.prob <- predict(glm.admit.fit, 
                                newdata = newdata1, 
                                type = "response"
                                )
newdata1
newdata1$admit1.pred <- rep(1,4)
newdata1$admit1.pred[newdata1$admit1.prob<0.5] <- 0
newdata1
```

Note that the above commands add two new columns to newdata1.

Or alternatively, we can use
```{r}
newdata2 <- data.frame(gre = mean(mydata$gre), gpa = mean(mydata$gpa), rank = factor(1:4))
newdata2$admit1.prob <- predict(glm.admit.fit, newdata = newdata2, type = "response")
newdata2
newdata2$admit1.pred <- rep(1,4)
newdata2$admit1.pred[newdata2$admit1.prob<0.5] <- 0
```

`with(data, expression)` applies an expression to a dataset.


For more exercises and more detailed explanations, please refer to https://stats.idre.ucla.edu/r/dae/logit-regression/.



