---
title: "Week 6 Lab Questions"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#### Question 1 - Bayesian network classifier#

<font size="6.0">Given a training dataset including two predictors (i.e. X1 and X2) and one class attribute (i.e. Y), please create the conditional probability tables (CPTs) according to the predictor dependencies shown in the Bayesian network, then predict the class label of the testing instances(observations).</font> 

#### Question 2 - Classification tree

Load the Titanic dataset.

```{r, message=FALSE, warning=FALSE}
library(readr)
library(dplyr)
library(tree)
titanic3 <- "https://goo.gl/At238b" %>%
read_csv %>% # read in the data
select(survived, embarked, sex, sibsp, parch, fare) %>%
mutate(embarked = factor(embarked), sex = factor(sex))
```


1) Survived is a numeric value. We need to first transform it to a categorical value. Use titanic3\$survived = as.factor(titanic3\$survived) to do so.

```{r, message=FALSE, warning=FALSE}

```

2) Fit a classification tree using all the instances. Find out which predictors actually contribute to building this tree. Plot the tree.

```{r, message=FALSE, warning=FALSE}

```
```{r, message=FALSE, warning=FALSE}

```


3) Now we are going to estimate the testing error:

a. Split the instances into a training dataset and a testing dataset (with set.seed(2)).
```{r, message=FALSE, warning=FALSE}

```
b. Build the tree using the training dataset, and plot the tree.
```{r, message=FALSE, warning=FALSE}

```

c. Evaluate its performance on the testing dataset.
```{r, message=FALSE, warning=FALSE}

```

4) Next, let’s find out whether pruning the tree might lead to improved results.
a. Use cv.tree() to determine the optimal level of tree complexity (with set.seed(21)).
```{r, message=FALSE, warning=FALSE}

```
b. According to the result, do you think pruning is necessary? Why or why not? The results show that the best tree has 5 or 4 leaves. There is no need to prune. But we can try to prune the tree to 4 leaves.
c. If you think it is necessary, or would like to give it a try, use prune.misclass() to prune the tree and evaluate the performance of the pruned tree.
```{r, message=FALSE, warning=FALSE}

```
```{r, message=FALSE, warning=FALSE}

```

