---
title: "Week 5 Lab Question Sheet"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### 1) Load the wine quality training dataset (available on moodle). Look at the summary of the training dataset. 

```{r, warning=F, message = F}

```

#### 2) Conduct 10-fold cross validation to obtain the average AUROC value by using alcohol as the only feature.

```{r, warning=F, message = F}

```

#### 3) Conduct 10-fold cross validation to obtain the average AUROC value by using residual.sugar as the only feature.

```{r, warning=F, message = F}

```

#### 4) Conduct 10-fold cross validation to obtain the average AUROC value by using alcohol and residual.sugar as features.

```{r, warning=F, message = F}

```

#### 5) What conclusions can we make based on the comparisons between the AUROC values obtained by those different combinations of features?


#### 6) Train three logistic regression classifiers by using the entire training dataset and different combinations of features. Evaluate the predictive accuracy of models by using the testing dataset (available on moodle).
```{r, warning=F, message = F}

```

