---
title: Week 1 Exercises
output:
  pdf_document: default
  html_document: default
 
---

**Vectors**

**1. Create a vector u that has values -10, -9, -8, . . . ,0. How many
different ways can you use?**
```{r}
u <- c(-10, -9, -8, -7, -6, -5, -4, -3, -2, -1, 0)
u <- c(-10:0)
u <- seq(-10,0, by=1)
print(u)
```


**2. Create another vector v that has values -0.1, 0.4, 0.9, 1.4, ., and
there are 11 numbers (aka**

**terms) in v. How many different ways can you use?**
```{r}
v <- seq(-0.1, by=0.5,length.out=11)
print(v)
```

**3. Calculate the vector of u+v and u\*v.**
```{r}
u_v <- u+v
u.v <- u/v
print(u_v)
print(u.v)
```


**4. Increase all terms in u by 1, and then take away 20% from all terms
in v.**
```{r}
u_plus <- u+1
v_20 <- v-0.2
print(u_plus)
print(v_20)
```


**5. Create a vector w that contains all the numbers from u and then v.
Report the length of**

**w.**
```{r}
w <- c(u,v)
print(w)
```


**6. Use a command to return the 14th, 15th and 16th value of w. What
about the 2nd, the**

**5th, 9th and 21st value of w? What is the 23rd value?**
```{r}
w.5 <- w[5]
w.9 <- w[9]
w.14 <- w[14]
w.15 <- w[15]
w.16 <- w[16]
w.21 <- w[21]
w.23 <- w[23]
print(w.5)
print(w.9)
print(w.14)
print(w.15)
print(w.16)
print(w.21)
print(w.23)
```


**7. Sort w in the descending order.**
```{r}
sort(w, decreasing = T)
```


**Matrices**

**1. Create the following matrix and assign it to the variable b_matrix.
Extract a sub-matrix**

**from b_matrix named subB.**
```{r}
b_matrix <- matrix(seq(1,39, by=2), 4,5,
                   byrow = T, 
                   dimnames = list(c("A", "B", "C", "D"), 
                                   c("a", "b", "c", "d", "e")))
b_matrix
subB <- b_matrix[c(1,2,4),c(2,3)]
subB
```

\## a b c d e

\## A 1 3 5 7 9

\## B 11 13 15 17 19

\## C 21 23 25 27 29

\## D 31 33 35 37 39

**2.** **Create three vectors x,y,z with integers and each vector has 3
elements.** **Combine the**
```{r}
x <- c(1,2,3)
y <- c(4,5,6)
z <- c(7,8,9)
x
y
z
```


**three vectors to become a** 3 *×* 3 **matrix A where each column
represents a vector. Change the row names to a,b,c.**
```{r}
A <- cbind(x,y,z)
rownames(A) <- c("a", "b", "c")
colnames(A) <- c("A", "B", "C")
A

B <- cbind(x,y,z)
rownames(B) <- c("a", "b", "c")
colnames(B) <- c("A", "B", "C")
B
```