---
title: "Week 1 Exercises"
output: pdf_document
---

# Vectors
### 1.	Create a vector u that has values -10, -9, -8, ...,0.  How many different ways can you use?
```{r}
u <- c(-10, -9, -8, -7, -6, -5, -4, -3, -2, -1, 0)
u <- -10:0
u <- seq(-10,0)
# In the following two lines, from = and to = can be omitted.
u <- seq(from = -10, to = 0, by = 1)
u <- seq(from = -10, to = 0, length.out = 11)
```
### 2.	Create another vector v that has values -0.1, 0.4, 0.9, 1.4, ., and there are 11 numbers (aka terms) in v. How many different ways can you use?
```{r}
v <- c(-0.1, 0.4, 0.9, 1.4, 1.9, 2.4, 2.9, 3.4, 3.9, 4.4, 4.9)
# In the following line, from = can be omitted.
v <- seq(from = -0.1, by = 0.5, length.out = 11)
print(v)
```
### 3.	Calculate the vector of u+v and u*v.
```{r}
u+v
u*v
```
### 4.	Increase all terms in u by 1, and then take away 20% from all terms in v.
```{r}
u+1
(1-0.2)*v
```
### 5.	Create a vector w that contains all the numbers from u and then v. Report the length of w. 
```{r}
w <- c(u,v)
print(w)
length(w)
```
### 6.	Use a command to return the 14th, 15th and 16th value of w. What about the 2nd, the 5th, 9th and 21st value of w? What is the 23rd value?
```{r}
w[14:16]
w[c(2,5,9,21)]
w[23]    # No error is reported, but a NA
```
### 7. Sort ```w``` in the descending order.
```{r}
sort(w, decreasing = T)
```
# Matrices
### 1. Create the following matrix and assign it to the variable `b_matrix`. Extract a sub-matrix from b_matrix named subB.
``` {r}
b_matrix <- matrix(
  seq(1,39,by=2),4,5,byrow=T,
  dimnames = list(
    c("A", "B", "C", "D"),
    c("a", "b", "c", "d", "e")
  ))
b_matrix
subB <- b_matrix[c(1,2,4),c(2,3)]
subB
```
### 2. Create three vectors  ```x,y,z```  with integers and each vector has 3 elements. Combine the three vectors to become a $3\times 3$ matrix  `A`  where each column represents a vector. Change the row names to  `a,b,c`.
```{r}
x <- c(1,2,3)
y <- c(4,5,6)
z <- c(7,8,9)
A <- cbind(x,y,z) 

rownames(A) <- c("a","b","c")
colnames(A) <- c("X","Y","Z")  #add column names
print(A)

#if combined by rows:
B <- rbind(x,y,z)
print(B)
```

